`make.events`

### 2021-01-11 inst/gitbook/04_make.events.Rmd
Create 04_make.events.Rmd

---
title: "`make.modifiers`"
author: "Thomas Guillerme (guillert@tcd.ie)"
date: "`r Sys.Date()`"
bibliography: [../References.bib, ../packages.bib]
output:
  html_document: default
  pdf_document: default
---

# Making modifiers with `make.modifiers()` {#makemodifiers}

@@

>>>>

---
title: "`make.events`"
author: "Thomas Guillerme (guillert@tcd.ie)"
date: "`r Sys.Date()`"
bibliography: [../References.bib, ../packages.bib]
output:
  html_document: default
  pdf_document: default
---

# Making events with `make.events()` {#makeevents}

@@

## Conditions

## Modifications

## Some events examples
